Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-01 PaperVictor.tex
Revise experimental details

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, p-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. Electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ (gravimetrically obtained), using current densities of 0.5 and 305 mA$/$%
cm$^{2}$, respectively. However, it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte diffusivity problems \cite{Ariza2011}.
For this reason, the current
densities were chosen as 35 and 305 mA$/$cm$^{2}$, with corresponding
porosities of 51$\%$ and 76$\%$, respectively. The calibration curves were
acquired through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions and were weighed ($m_{i}$)
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to calculate
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}. Etching
rate of PS was obtained by re-synthetizing individual layers under similar
conditions and measuring their thicknesses through SEM (Scanning Electron
Microscopy). The absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident angles $%
\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $%
50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

This section presents the comparison of the calculated and measured reflectance
spectra at different incidence angles in the regions of interest. In the first
subsection, the design and optimization of R$_{\text{ave}}$ of \textit{chirped}
photonic structures is presented, and next subsection the design of the structure is
analyzed through sub-mirrors stacks.

\subsection{Chirped-type Bragg mirrors}

>>>>

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de
  aquí, pues lo discutes abajo:(gravimetrically obtained)}, using
current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$,
respectively. However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, with
corresponding
porosities of 51\% and 76\%, respectively. The porosity was calibrated
\notaL{Creo que no muestras curvas de calibración: calibration curves were
acquired} through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions applying a constant
current for a time \notaL{cuánto tiempo para la calibración?}  and were weighed to
obtain their mass $m_i$
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to obtain
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.
The etching
rate of PS was obtained by synthetizing single layers under similar
conditions and measuring their thicknesses through Scanning Electron
Microscopy (SEM). Absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident
angles $\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$,
$40^{\circ }$, $50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

In this section we present compare the calculated and measured reflectance
spectra at different incidence angles in the regions of interest. In the first
subsection, the design and optimization of R$_{\text{ave}}$ of \textit{chirped}
photonic structures is presented, and next subsection the design of the structure is
analyzed through sub-mirrors stacks.

\notaL{Quizás esto se pueda incluir por aquí.:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
}
\subsection{Chirped-type Bragg mirrors}
